Quick Research Review

### 2019-02-12 presentations/weeklies/meeting_190205.tex
reorg meetings
compute reflectivity(t)
plot Ri(nu), R(nu), explore Ri-R?

    Had great $u_z$ fits including viscosity (error $\sim 3-5\%$), but did not
    show great $S_{px}(z; \nu)$ fits last week. Here they are!
    \begin{figure}[t]
        \centering
        \includegraphics[width=0.7\textwidth]{../sims/2d_3_final/snapshots_lin_1/fluxes.png}
        \caption{Fits linear $S_{px}(z; \nu)$.}
    \end{figure}
\end{frame}

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../sims/2d_3_final/snapshots_nl_4/fluxes.png}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item Last week: Evolution of $\ev*{u_x}_x(t),
                    \ev*{S_{px}}_x(t)$ at different times. Note flux seems to
                    decrease over time throughout domain.

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../sims/2d_3_final/snapshots_nl_1/fluxes.png}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item More damped for comparison ($\nu \to 7\nu/3$).

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../sims/2d_3_final/snapshots_nl_4/front.png}
            \end{figure}
            \begin{itemize}
                \item Three different $\Delta S_{px}$:
                    \begin{itemize}
                        \item LinVisc extrapolate $S_{px, 0}$.

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../sims/2d_3_final/snapshots_nl_1/front.png}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item Overdamped for comparison.

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../sims/2d_3_final/snapshots_nl_4/fft.png}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item FT of $\delta \vec{u}$ slightly below the critical layer.
                    Red line denotes where $2\nu k_x^2 = \omega$, ``viscous
                    wavenumber''?

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../sims/2d_3_final/snapshots_nl_1/fft.png}
                \caption{Overdamped for comparison, not power law!}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../sims/2d_3_final/snapshots_lin_2/fft.png}
                \caption{Linear for comparison; taken just below damping zone.}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../sims/2d_3_final/snapshots_nl_4/p_009.png}
                \caption{Residuals for not overdamped. }
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../sims/2d_3_final/snapshots_nl_1/p_009.png}
                \caption{Residuals for overdamped.}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

>>>>

    Had great $u_z$ fits including viscosity (error $\sim 3-5\%$), but did not
    show great $S_{px}(z; \nu)$ fits last week. Here they are!
    \begin{figure}[t]
        \centering
        \includegraphics[width=0.7\textwidth]{../../sims/2d_3_final/snapshots_lin_1/fluxes.png}
        \caption{Fits linear $S_{px}(z; \nu)$.}
    \end{figure}
\end{frame}

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_4/fluxes.png}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item Last week: Evolution of $\ev*{u_x}_x(t),
                    \ev*{S_{px}}_x(t)$ at different times. Note flux seems to
                    decrease over time throughout domain.

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_1/fluxes.png}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item More damped for comparison ($\nu \to 7\nu/3$).

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_4/front.png}
            \end{figure}
            \begin{itemize}
                \item Three different $\Delta S_{px}$:
                    \begin{itemize}
                        \item LinVisc extrapolate $S_{px, 0}$.

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_1/front.png}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item Overdamped for comparison.

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_4/fft.png}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item FT of $\delta \vec{u}$ slightly below the critical layer.
                    Red line denotes where $2\nu k_x^2 = \omega$, ``viscous
                    wavenumber''?

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_1/fft.png}
                \caption{Overdamped for comparison, not power law!}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_lin_2/fft.png}
                \caption{Linear for comparison; taken just below damping zone.}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

@@

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_4/p_009.png}
                \caption{Residuals for not overdamped. }
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_1/p_009.png}
                \caption{Residuals for overdamped.}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

### 2019-02-12 presentations/weeklies/meeting_190212.tex
reorg meetings
compute reflectivity(t)
plot Ri(nu), R(nu), explore Ri-R?

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item Linear: $\nu = 0$ has $S_{px}(z) = S_{px, 0}$ great
                    prediction. Fit $\vec{u}$ for $\nu \neq 0$ as well, though
                    not $S_{px}(z)$ yet (\textbf{Updated!}).

                \item In nonlinear, review: expect deposited flux $\Delta S_{px}
                    = S_{px, 0}$ incident/generated flux.

                \item Instead, observe $\Delta S_{px} < S_{px, 0}$, and moreover
                    $S_{px}$ far from critical layer changing over time!
            \end{itemize}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item Last week: defined some
                    \begin{equation}
                        \delta u_z = \frac{u_z - u_{z, 0}
                            - \ev*{u_z}_x}{\abs*{u_{z, 0}}},
                    \end{equation}
                    deviation (new: subtracting mean flow too), computed RMS\@.
                    Found higher RMS for lower $\nu$.

                \item Could it be $\ev*{\dots}_x$ vs $\ev*{\dots}_t$?

                \item Objective: understand ``reflection''?
            \end{itemize}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Overview}

    \begin{itemize}
        \item Understand exactly how much flux is being absorbed at the critical
            layer:
            \begin{itemize}
                \item Can the decreased flux absorption be explained by
                    viscous dissipation before the critical alyer alone?

                \item Compare predictions of $\pd{z_c}{t}$ to the observed
                    $\Delta S_{px}$ at the critical layer.
            \end{itemize}

        \item Understand nature of ``reflection'', why cannot see in certain
            simulations.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Results}
    \framesubtitle{Linear}

    Had great $u_z$ fits including viscosity (error $\sim 3-5\%$), but did not
    show great $S_{px}(z; \nu)$ fits last week. Here they are!
    \begin{figure}[t]
        \centering
        \includegraphics[width=0.7\textwidth]{../../sims/2d_3_final/snapshots_lin_1/fluxes.png}
        \caption{Fits linear $S_{px}(z; \nu)$.}
    \end{figure}
\end{frame}

\begin{frame}
    \frametitle{Results}
    \framesubtitle{Mean Flow and Flux}

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_4/fluxes.png}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item Last week: Evolution of $\ev*{u_x}_x(t),
                    \ev*{S_{px}}_x(t)$ at different times. Note flux seems to
                    decrease over time throughout domain.

                \item Bottom panel, solid lines are time slices, dotted lines
                    indicate averaging over $\sim \frac{2\pi}{\omega}$ one
                    period (6 times), thick line is linear viscous prediction.

                \item Shaded grey indicates one vertical wavelength.
            \end{itemize}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Results}
    \framesubtitle{Mean Flow and Flux}

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_1/fluxes.png}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item More damped for comparison ($\nu \to 7\nu/3$).

                \item Note that $S_{px}$ does not change much over time, general
                    trend matches viscous linear decrease.
            \end{itemize}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Results}
    \framesubtitle{Absorbed Flux and Front Propagation}

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_4/front.png}
            \end{figure}
            \begin{itemize}
                \item Three different $\Delta S_{px}$:
                    \begin{itemize}
                        \item LinVisc extrapolate $S_{px, 0}$.

                        \item $\Delta S_{px; S}$ ($z$-avg).

                        \item $\Delta S_{px; U}$ ($z$-avg too).
                    \end{itemize}
            \end{itemize}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}

                \item \textbf{FIXED} $z_c(t)$ for different incident fluxes,
                    even more models:
                    \begin{itemize}
                        \item Solid lines are three ways of extracting from
                            data.

                        \item Dotted lines use $\pd{z_c}{t}(\Delta S_{px})$
                            model for three values of $S_{px}$:
                            \begin{itemize}
                                \item Average $\Delta S_{px}$.
                                \item $\nu$-extrapolated $S_{px, 0}$.
                                \item Full $S_{px, 0}$.
                            \end{itemize}
                    \end{itemize}
                    Takeaway: strongly inconsistent with $S_{px, 0}$ being
                    completly absorbed! In fact, most are $\sim 0.5S_{px}$ being
                    absorbed.
            \end{itemize}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Results}
    \framesubtitle{Absorbed Flux and Front Propagation}

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_1/front.png}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item Overdamped for comparison.

                \item Absorbed flux is in good agreement w/ linear viscous
                    extrapolation of $S_{px, 0}$, seems to imply full
                    absorption.
            \end{itemize}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Results}
    \framesubtitle{Absorbed Flux and Front Propagation}

    \begin{table}[t]
        \centering
        \begin{tabular}{c c c}
            $\nu$ & $\Delta S_{px; S}$ & LinVisc Extrapolation\\\midrule
            $0.7\nu_0$ & $0.55$ & $0.52$\\
            $0.4\nu_0$ & $0.54$ & $0.66$\\
            $0.4\nu_0$ (double strength) & $0.42$ & $0.56$\\
            $0.3\nu_0$ & $0.51$ & $0.71$\\
            $0.2\nu_0$ & $0.47$ & $0.76$\\
            $0.1\nu_0$ & $0.45$ & $0.82$
        \end{tabular}
        \caption{Fluxes in units of $S_{px, 0}$ excited flux. For linear viscous
        extrapolation, I took a slightly earlier (but not immediate) flux and
        extrapolated to an average $z_c$, so rather approximate.}
    \end{table}
\end{frame}

\begin{frame}
    \frametitle{Results}
    \framesubtitle{Residual Flow Properties}

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_4/fft.png}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item FT of $\delta \vec{u}$ slightly below the critical layer.
                    Red line denotes where $2\nu k_x^2 = \omega$, ``viscous
                    wavenumber''?

                \item Note that we've chosen $\nu k_x^2 \lesssim u_xk_x \sim
                    \frac{\omega}{k_{0x}}k_x$, our previous viscous wavenumber
                    already.
            \end{itemize}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Results}
    \framesubtitle{Residual Flow Properties}

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_1/fft.png}
                \caption{Overdamped for comparison, not power law!}
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_lin_2/fft.png}
                \caption{Linear for comparison; taken just below damping zone.}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

\begin{frame}
    \frametitle{Useful Plots}
    \framesubtitle{Residuals}

    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_4/p_009.png}
                \caption{Residuals for not overdamped. }
            \end{figure}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{figure}[t]
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_1/p_009.png}
                \caption{Residuals for overdamped.}
            \end{figure}
        \end{column}
    \end{columns}
\end{frame}

>>>>

    \begin{itemize}
        \item Last time: found flux absorbed $\neq$ flux injected w/
            $\nu$-extrapolation, \textbf{must have reflection.}

        \item Hypothesis:
            \begin{equation}
                \vec{u} = A_0\vec{u}_0 + \delta \vec{u},
            \end{equation}
            where $A_0$ is set by forcing, $\delta \vec{u}$ is ``turbulent.''

        \item Since $S_{px} = \ev*{\rho u_xu_z}_x$, decided to plot
            \begin{equation}
                \delta S_{px} = \ev*{\rho \delta u_x \delta u_z}_x.
            \end{equation}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Results}
    \framesubtitle{Driving amplitude}

    \begin{itemize}
        \item Actually, discovered $A < A_0$, \textbf{driving amplitude changes
            over time} (via convolution). Oscillation timescale $\sim
            \frac{z_0 - z_c}{v_{gz}}$ for higher order modes.

        \item Adjusting for this gives $\ev*{\rho u_{x0} \delta u_z}_x,
            \ev*{\rho \delta u_x u_{z0}}_x$ centered on zero, no net flux.

        \begin{figure}[t]
            \centering
            \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_lin_1/f_amps.png}
                \caption{Linear excited $\frac{u_x}{u_{x0}}, \frac{u_z}{u_{z0}}$ over
                time.}
            \end{subfigure}
            \begin{subfigure}{0.45\textwidth}
                \centering
                \includegraphics[width=\textwidth]{../../sims/2d_3_final/snapshots_nl_4/f_amps.png}
                \caption{Nonlinear excited $\frac{u_x}{u_{x0}}, \frac{u_z}{u_{z0}}$ over
                time.}
            \end{subfigure}
        \end{figure}
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Results}
    \framesubtitle{Driving Amplitude}

    \begin{figure}[t]
        \centering
        \includegraphics[width=0.6\textwidth]{../../sims/2d_3_final/snapshots_nl_4/fluxes_time.png}
        \caption{Decompositions of the flux over time. $01$ means $u_{x0} \delta
        u_z$. Oscillating $01, 10$ implies reflected $k_z \to -k_z$ mode.}
    \end{figure}
\end{frame}

\begin{frame}
    \frametitle{Results}
    \framesubtitle{Front Position}

    \begin{figure}[t]
        \centering
        \includegraphics[width=0.6\textwidth]{../../sims/2d_3_final/snapshots_nl_4/front.png}
        \caption{Front evolution, nonlinear.}
    \end{figure}
\end{frame}

\begin{frame}
    \frametitle{Results}
    \framesubtitle{Minimum Ri}

    \begin{figure}[t]
        \centering
        \includegraphics[width=0.6\textwidth]{../../sims/2d_3_final/snapshots_nl_4/fluxes.png}
        \caption{Mean flow and flux evolution, non-linear.}
    \end{figure}
\end{frame}

\begin{frame}
    \frametitle{Conclusion}
    \framesubtitle{All effects}

    \begin{itemize}
        \item Excite wave with $S_{px}$. Deposit some $\eta S_{px}$ in
            critical layer (efficiency $\eta$).

        \item Critical layer width $\delta z$ such that $\mathrm{Ri} \gtrsim
            \frac{1}{4}$.

        \item Critical layer position obeys $\rho c_{ph, x} \pd{z_c}{t}
            = -\eta S_{px}$, or ($\tau = \frac{H\rho_0(z = 0)c_{ph,x}}
            {\eta S_{px}}$)
            \begin{equation}
                z_c(t) = -H\ln \frac{t - t_i + \tau e^{-z_i/H}}{\tau},
            \end{equation}

        \item Reflect $(1 - \eta)S_{px}$, some in $k_z \to k_z$ linear
            reflection, some in higher-order modes.

        \item Reflected wave causes inefficient excitation $S_{px,0} \to \alpha
            S_{px, 0}$, $\alpha \lesssim 1$.

        \item Probably can't be any more exact, time delays + noisy data.
    \end{itemize}
\end{frame}
